---
title: "Untitled"
author: "Shu"
date: "21/10/2020"
output: html_document
---

```{r setup, include=FALSE}

rm(list=ls()) # Clear workspace. 
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(GGally)
library(car)
library(caret)
library(DMwR)
library(pROC)
library(ggplot2)     
```
The whole data analysis process contains 5 steps in this project: 1. Data Cleaning; 2. Data Analyse; 3. Train and test set split; 4. Balance Data; 5. Modeling Data; 6. Model Selection.
The details can be found in the report.
```{r}
#Read dataset into R.
insurance <- read.csv('train.csv')
```

```{r}
#A quick look of the data.
head(insurance,5)
```

```{r}
# See if there is any missing values.
sum(is.na(insurance))
```
```{r}
#A fucntion to find special values.
is.special <- function(x){
if (is.numeric(x)) !is.finite(x) else is.na(x)
}
```

```{r}
#Find number of special values if there's any.
sum(sapply(insurance, is.special))
```

```{r}
#An overview of data for checking consistency.
summary(insurance)
```

```{r}
#Revalue the dependent variable "Response" for better graph.
insurance %>% 
  mutate(
    Response=factor(Response, levels=c(0,1), labels=c("Not_Interested", "Interested")),
    Previously_Insured=factor(Previously_Insured),
    Driving_License=factor(Driving_License),
    Region_Code=factor(Region_Code),
    Vehicle_Age=factor(Vehicle_Age),
    Vehicle_Damage=factor(Vehicle_Damage)
  ) ->insurance.revalued
```

```{r}
#Visualize responses in "Previously_Insured"
ggplot(data=insurance.revalued, aes(x=Previously_Insured, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")

```




```{r}
#"Previously_Insured" is a lurking variable, and now excluded observations with "Previously_Insured"==0 and id before continuing.
insurance.revalued %>%
  filter(Previously_Insured=="0") %>%
  select(2:12)-> insurance.revalued.a
```
Each independent variable is plotted in bar chart and filled with "Response" in two levels：'Interested' and 'Not_Interested'
```{r}
ggplot(data=insurance.revalued.a, aes(x=Age, fill=factor(Response))) +geom_histogram(bins = 90)+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued.a, aes(x=Gender, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued.a, aes(x=Driving_License, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")

prop.table(table(insurance.revalued$Driving_License))
```

```{r}
ggplot(data=insurance.revalued.a, aes(x=Region_Code, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")
```


```{r}
ggplot(data=insurance, aes(x=Vehicle_Age, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued, aes(x=Vehicle_Age, fill=factor(Previously_Insured))) +geom_bar(width = 0.5)+
labs(fill = "Previously_Insured")
```
```{r}
ggplot(data=insurance.revalued.a, aes(x=Vehicle_Damage, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued.a, aes(x=Annual_Premium, fill=factor(Response))) +geom_histogram(bins=60)+
labs(fill = "Response")
```

```{r}
#Found outliers in "Annual_Premium", so value that is more than 100000 is taken out.
insurance.revalued.b <- subset(insurance.revalued.a,insurance.revalued.a$Annual_Premium< 1*10^5)
```


```{r}
#A better view of data without outliers.
ggplot(data=insurance.revalued.b, aes(x=Annual_Premium, fill=factor(Response))) +geom_histogram(bins=60)+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued.b, aes(x=Policy_Sales_Channel, fill=factor(Response))) +geom_histogram()+
labs(fill = "Response")
```
```{r}
ggplot(data=insurance.revalued.b, aes(x=Vintage, fill=factor(Response))) +geom_histogram(binwidth = 0.5)+
labs(fill = "Response")
```


```{r}
#Categorical variable should be concerted to factors.
insurance %>% 
  mutate(
    Gender=factor(Gender),
    Response=factor(Response),
    Previously_Insured=factor(Previously_Insured),
    Driving_License=factor(Driving_License),
    Region_Code=factor(Region_Code),
    Vehicle_Age=factor(Vehicle_Age),
    Vehicle_Damage=factor(Vehicle_Damage),
    Policy_Sales_Channel=factor(Policy_Sales_Channel)
  ) ->insurance.factored
```

```{r}
# Let's make this randomness reproducible
set.seed(123) 

# Sample from the row numbers without replacement
training.rows <- sample(1:nrow(insurance.factored), 0.8 * nrow(insurance.factored))

# Split the insurance data into training and test
training.t <- insurance.factored[ training.rows,]
testing.t <- insurance.factored[-training.rows,]
```


```{r}
#Check ratio of dependent variable,interested vs not interested is nearly 1:9, the data is imbalanced.
prop.table(table(training$Response))
```
Balance training set. Using SMOTE to balance more than 260000 observations is time consuming, it takes 20 minutes. So, once it's been produced, should be write into a new csv file for convenient.
```{r}
# training <- SMOTE(Response ~ Gender + Age + Driving_License + Region_Code + Previously_Insured + Vehicle_Age + Vehicle_Damage +
#                     Annual_Premium + Policy_Sales_Channel + Vintage
#                   ,training, perc.over = 100,perc.under=200)
```

```{r}
# write.csv(training,"balanced.insurance.train.csv", row.names = FALSE)
```

```{r}
 training <- read.csv('balanced.insurance.train.csv')
```


```{r}
#Recheck the ratio, interested vs not interested is  1:1.
prop.table(table(training$Response))
```

```{r}
#Recheck on lurking variable "Previously_Insured", balanced data fixed the problem. 
ggplot(data=training, aes(x=Previously_Insured, fill=factor(Response))) +geom_bar(width = 0.5)+
labs(fill = "Response")
```




```{r}
#Use rpart for Decision Tree. The predictors involved were concluded by graphs above.
library(rpart)
model_rf = rpart(training$Response ~Vehicle_Damage+Age+Policy_Sales_Channel+Previously_Insured+Vehicle_Age, data = training, control = rpart.control(cp = .0005))
```




```{r}
tree_pred = predict(model_rf, testing, type='prob')
```

```{r}
#Use ROC and AUC as metrics to test prediction.Plot ROC curve.
library(ROCR)
pred <- prediction(tree_pred[,2], testing$Response)
perf <- performance(pred, "tpr","fpr") 
plot(perf, col = rainbow(10))
```


``````{r}
#Calculate AUC for Decision Tree model.AUC = 0.79.
auc <- performance(pred, measure = "auc")
auc <- auc@y.values[[1]]
auc
```


```{r}
#Use same predictors for Logistic Regression model.
Response.glm.training <- glm(Response ~Vehicle_Damage+Age+Policy_Sales_Channel+Previously_Insured+Vehicle_Age, data=training, family="binomial")
```

```{r}
#Have a look of p-values, AIC and deviance.
summary(Response.glm.training)
```
```{r}
#Check for multicollinearity
vif(Response.glm.training)
```


```{r}
#Use ROC and AUC to test Logistic Regression.Plot ROC curve.
p <- predict(Response.glm.training, testing, type="response")
pr <- prediction(p, testing$Response)
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf, col = rainbow(10))
```
```{r}
#AUC = 0.80
auc <- performance(pr, measure = "auc")
auc <- auc@y.values[[1]]
auc
```

